---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
    latex_engine: xelatex
---

```{r rsetup,eval=TRUE,include=FALSE}
require("codecheck")
require("knitr")
require("rprojroot")
require("yaml")
require("xtable")
require("tibble")
require("readr")
options(width = 60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df = copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path = FALSE,
                                  overwrite = FALSE
                                  )
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```

# Summary


This codecheck happened in two parts; the first part was as part of
the Delft workshop in May 2024.  The author was present whilst several
participants worked on the project.  There were some initial issues
around operating system compatibility (e.g. path separators), but
these were fixed during the workshop.

After the workshop, one of us (SJE) worked on repeating the work and
writing this up.  

Our conclusion is that work is clearly reproducible.

\clearpage

# CODECHECKER notes



This project was written mostly in python, with some matlab for
plotting purposes.  The project README was mostly clear to follow,
although  discussions with the author helped to clarify that the only
file that needs to contain data is ROOT/results_rad_imp with the other
two folders (ROOT/results_diff_imp and ROOT/results_opt_imp) starting
as empty directories.

## Installation

Matlab 2024b was available; we needed to install the npy-matlab
package

```
cd ~/proj/2020/codecheckers/Inter_Noise2024_Codes_Acoustics_Diffusion_Equation

gh repo clone kwikteam/npy-matlab

start matlab and then

addpath('/Users/stephen/proj/2020/codecheckers/Inter_Noise2024_Codes_Acoustics_Diffusion_Equation/npy-matlab/npy-matlab')  
savepath
```



## Running


Perhaps the most challenging thing was to work out how to make the
parameter settings required to generate each figure.  The approach herer was
to come up with a set of versions of the original script
ROOT/1-DiffEq3D.py for each folder.  These are stored in the codecheck
folder and titled 1-DiffEq3d-runN.py where N represents the run
number.  In the codecheck folder, there is also a shell-script that
runs all the steps required for each figure.  For example
codecheck/run1.sh will run all the steps for the first run.


| Run | To generate which figures | Approximate time |
|:----|:--------------------------|:-----------------|
| 1   | Figure 1                  | 5 minutes        |
| 2   | Figure 2, 5               | 15 minutes       |
| 3   | Figure 3                  | 2 minutes        |
| 4   | Figure 4                  | 15 minutes       |
| 5   | Figure 7                  | 15 minutes       |


The run-times are approximate; figure 3 was the smallest room, so was
quickest to run.  Run 1 was simpler as it didn't require the
optimization steps (as noted in the README).



## Reproducibilility

We managed to reproduce all the figures from the paper.  There are
some trivial differences (e.g. axis labels, some titles) which are
presumably accounted for interactive editing of the figures, rather
than anything substantial.  Issues with figure labels aside, the only
noticeable difference observed was that the solid line in Figure 1a is
around 87.4 in the manuscript versus our value here of around 87.8;
this was presumably a small difference in some settings and not a
concern.


### Figures 6 and 8

Figures 6 and 8 were reproducible from the matlab code, although it is
worth clarifying that these figures used the data files that were
provided in the author's repository, rather than using the versions
that generated by the codechecker.  Given that other figures could be
reproduced, there is no reason to doubt that the data underlying fig 6
and 8 is reproducible.



## Recommendations

We suggest to the authors to consider the following suggestions for their next publication or workflow:

### Separate out parameters from the scripts

Various settings for the program (e.g. lines 33-46) needed to be
change to generate the different figures.  Consider whether the
parameters could be set in their own file, separate from other
elements.  This would make it easier for running your work under
different conditions.

### Matlab dependency

Whilst there is nothing wrong with matlab, the workflow would have
been slightly easier had all the plotting been done in Python, rather
than matlab.



\clearpage

# Manifest files

```{r, echo=FALSE, results="asis", width=100}
for(i in c(1:nrow(manifest_df))) {
  path <- manifest_df[i,"dest"]
  if(stringr::str_ends(path, "(png|pdf|jpg|jpeg)")) {
    # include graphics with knitr has to happen at top level in chunks, see https://github.com/yihui/knitr/issues/1260
    # see also https://stackoverflow.com/questions/51268623/insert-images-using-knitrinclude-graphics-in-a-for-loop
    # knitr::include_graphics(manifest_df[1, "dest"], error = TRUE)
    # Therefore, generate Markdown code here:
    cat("## ", basename(path), "\n\n")
    cat("**Comment:** ", manifest_df[i,"comment"], "\n\n")
    cat(paste0("![", "Test ", "](", path, ")\n"))
  } else if (stringr::str_ends(path, "(Rout|txt)")) {
    cat("## ", basename(path), "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    cat(readLines(path), sep = "\n")
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "csv")) {
    cat("## ", basename(path), "\n\n", "Summary statistics of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(skimr::skim(read.csv(path)))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else {
    cat("## ", basename(path), "\n\n")
    cat("Cannot inlcude output file as figure.")
  }
  
  cat("\\clearpage \n\n")
}
```

\clearpage

## Acknowledgements

Thank you to the Ilaria for her patience whilst this codecheck was
being performed.  We would like to acknowledge NWO for funding the
CHECK-NL project, and enabling the initial workshop at Delft.


# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```


